### 2018-03-15 Paper/jaccardbaetica.tex
add new changes bib
add new changes conclusion

%hablar un poco del comercio del aceite de oliva quizás citando el paper de Williams, Peacok y mattlingly el colega

@@

@@

No strong relation between stamps and spatial distance have been detected in amphora workshops.  
Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only few similar stamps between closer amphora workshops were found.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are shareable stamps in closer workshops. Probably same stamps detected in closer amphora workshop could have been wrongly catalogued twice in different way in spite of belonging to the same place or being closer between each other.

%los que aparecen cerca son porque están cerca o puede haber confusión entre talleres

By contrast, we have located different stamps in a same amphora workshop. Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Rather our results could be interpreted due to several reason according to previous hypotheses. On the one hand, the use of these amphoric stamps could be exclusively running by the owner or family to distinguish the amphora workshop (CITAR).

(aumentar)
Considering that Dressel 20 type was not marked in several cases (CITAR) it can be interpreted somehow a batch systematic organization to prepare and distribute the commodity (CITAR)

@@

As summary, this method presented here highlights

@@

The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to 
All data has been analysed and conducted in R program version 3.2.4, using vegan package (citar)

>>>>

%hablar un poco del comercio del aceite de oliva quizás citando el paper de Williams, Peacok y mattlingly el colega
%hablar de las tres áreas de producción: hispalis, corduba y astigi

@@

Aquí poner algo sobre esto \citep{remesal_anforas_2004}

@@

No strong relation between stamps and spatial distance have been detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only few similar stamps between closer amphora workshops were found. In any case, our results show that most similar amphoric stamps were detected in closer workshops and not in other areas. These stamps tend to share the same area of production but there is not relation of similarity in general.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are similar stamps in closer workshops. Rather the stamps detected in closer amphorae workshops seem not move from other farthest workshops. Additionally they could have been "wrongly" catalogued twice in different mode in spite of belonging to the same place or being closer between each other. 
%los que aparecen cerca son porque están cerca o puede haber confusion entre talleres

By contrast, we have located different stamps in a same amphora workshop. Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Probably our results could be interpreted due to several reason according to previous hypotheses. The use of these amphoric stamps could be exclusively running by the owner or family to distinguish the amphora workshop (CITAR).

(aumentar)
On the other hand, it can be interpreted somehow a batch systematic organization to prepare and distribute the commodity considering that Dressel 20 type was not marked in several cases (CITAR)

@@

As summary, this method presented here provides a potential tool to understand mechanisms of production based on the similarity of artefacts.  This method have identified

highlight

@@

The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon. 
All data has been analysed and conducted in R program version 3.2.4, using vegan package (citar)
